PHQ4R - Data Cleaning

### 2024-01-06 study2/analysis/1_cleaning.qmd
add cleaning

@@

```{r}
# Consecutive count of participants per day (as area)
df |>
  mutate(
    Date = as.Date(Date, format = "%d/%m/%Y"),
    N = 1:nrow(df)
  ) |>
  ggplot(aes(x = Date, y = N)) +
  geom_area() +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Recruitment History",
    x = "Date",
    y = "Total Number of Participants"
  ) +
  see::theme_modern()
```

@@

```{r}
table1 <- df |> 
  select(Age, 
         PHQ4_Condition, 
         STAI5 = STAI5_General,
         BDI2 = BDI2_Total) |> 
  report::report_sample(group_by = "PHQ4_Condition")

@@

```{r}
rbind(
  as.data.frame(report::report(t.test(df$Age ~ df$PHQ4_Condition))),
  as.data.frame(report::report(t.test(df$STAI5_General ~ df$PHQ4_Condition))),
  as.data.frame(report::report(t.test(df$BDI2_Total ~ df$PHQ4_Condition)))
) |> 
  select(Parameter, t, df_error, p) |> 
  mutate(Parameter = str_remove_all(Parameter, fixed("df$"))) |>
  insight::display()
```

>>>>

```{r}
# Consecutive count of participants per day (as area)
df |>
  mutate(Date = as.Date(Date, format = "%d/%m/%Y")) |> 
  arrange(Date) |>
  mutate(N = 1:nrow(df)) |>
  ggplot(aes(x = Date, y = N)) +
  geom_area() +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Recruitment History",
    x = "Date",
    y = "Total Number of Participants"
  ) +
  see::theme_modern()
```

@@

@@

```{r}
table1 <- df |> 
  select(Age, 
         PHQ4_Condition, 
         PHQ4 = PHQ4_Total,
         STAI5 = STAI5_General,
         BDI2 = BDI2_Total) |> 
  report::report_sample(group_by = "PHQ4_Condition")

@@

```{r}
rbind(
  as.data.frame(report::report(t.test(df$Age ~ df$PHQ4_Condition))),
  as.data.frame(report::report(t.test(df$PHQ4_Total ~ df$PHQ4_Condition))),
  as.data.frame(report::report(t.test(df$STAI5_General ~ df$PHQ4_Condition))),
  as.data.frame(report::report(t.test(df$BDI2_Total ~ df$PHQ4_Condition)))
) |> 
  select(Parameter, t, df_error, p) |> 
  mutate(Parameter = str_remove_all(Parameter, fixed("df$"))) |>
  insight::display()
```
